---
title: "Getting Started with stance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with stance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

`stance` provides two complementary continuous decoding algorithms for fMRI data:

* **Continuous Linear Decoder (CLD)** – a fast deterministic approach using GLM+SVD and FISTA.
* **Continuous Bayesian Decoder (CBD)** – a probabilistic model with a hidden Markov prior and low-rank spatial factors.

This vignette demonstrates basic usage of both methods and offers guidance on choosing between them.

## Simulated Data

```{r}
library(stance)

# simulate small dataset
sim <- simulate_fmri_data(V = 200, T = 100, K = 3, algorithm = "CBD")
```

## Continuous Linear Decoder

```{r}
cld <- ContinuousLinearDecoder$new(
  Y = sim$Y,
  S_design = sim$S,
  hrf = "spmg1",
  rank = 10,
  lambda_tv = 0.01,
  verbose = TRUE
)
cld$fit(max_iter = 50)
plot(cld, type = "convergence")
```

## Continuous Bayesian Decoder

```{r}
cbd <- ContinuousBayesianDecoder$new(
  Y = sim$Y,
  K = 3,
  r = 10,
  hrf_basis = "canonical"
)
cbd$fit(max_iter = 50)
cbd$plot_convergence()
```

## Choosing Between CLD and CBD

Use **CLD** when a reliable design matrix is available and fast deterministic estimation is desired. Choose **CBD** when state boundaries are unknown or when uncertainty estimates about the latent states are important.


